Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-26 ApproximateCode.tex
Paper submittion!

To address this challenge, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems. The key idea of Approximate Code is distinguishing the important and unimportant data with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to ensure high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 4.7X when double disks fail.
\end{abstract}

@@

\section{Introduction}
For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used. Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, tip}. RS-based codes are encoded based on the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost. XOR-based codes simplify the computation, but they suffer other issues like scalability \cite{wu2012sdm, jiang2016bdr}.

@@

STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.
In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which leads to a long parity chain.

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} For example, in the diagonal parity $S = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S$.]{
\includegraphics[height=6.3cm, width = 3.8cm]{photo/STAR.pdf}\label{fig-star}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} For example, in the horizontal parity $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$]{
\includegraphics[height=6.3cm, width = 3.8cm]{photo/TIP.pdf}\label{fig-tip}
}\vspace{-3mm}
\caption{\small{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$.}}
\vspace{-3mm}
\label{fig-star-tip}
\end{figure}

TIP-Code is also an XOR-based 3DFTs erasure code.
Compared with STAR code, the parities are generated independently, which reduces the number of I/O operations for partial stripe writes.

@@

\begin{table}[ht]\small
\centering
\caption{
Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|p{2cm}<{\centering}|p{1.2cm}<{\centering}|p{1cm}<{\centering}|p{1.1cm}<{\centering}|p{1.1cm}<{\centering}|}
\hline
Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
Data Compression & low & / & high & \begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} \\ \hline
RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
RAID-6 & low & low & low & \\ \cline{1-4} 
RAID-5 & medium & medium & low & \\ \cline{1-4} 
Approximate Storage & very low & very low & low & \\ \cline{1-4} 
Approximate Code & low & high & low & \\ \hline
\end{tabular}
\vspace{-5mm}
\end{table}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=0.8\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}\label{fig-framework}
\vspace{-2mm}
\end{figure*}

@@

\subfigure[The generation of APPR.LRC ($4,2,2,3$,Even)]{
    \includegraphics[width=0.75\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
}
\caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
\vspace{-3mm}
\end{figure}

@@

\begin{figure}[ht]
\vspace{-3mm}
\centering
\subfigure[Structure selection.]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-STAR-STR.pdf}
}

\subfigure[Generation of APPR.STAR.]{
    \label{fig-ap-tip-GEN}
    \includegraphics[width = 0.95\linewidth]{photo/APPR-STAR-GEN.pdf}
}\vspace{-3mm}
\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}\label{fig-appr-star}
\vspace{-3mm}
\end{figure}

\begin{figure}[ht]
\centering
\subfigure[Structure selection of APPR.TIP-Code]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
}
\hspace{2pt}
\subfigure[Generation of local parities]{
    \label{fig-ap-tip-lP}
    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
}

\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.9\linewidth]{photo/APPR-TIP-GL-v2.pdf}
}
\vspace{-3mm}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}\label{fig-ap-TIP}
\vspace{-3mm}
\end{figure}

@@

\section{Evaluation}\label{evaluation}
In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code.
\subsection{Evaluation Methodology}
The experiment is divided into two parts: the first part evaluates the performance of the Approximate Code, and the second part evaluates the impact of the loss of the unimportant data on the video files.

In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP-Code. Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.

In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.

\subsubsection{Metrics}
We use the \textbf{Storage Efficiency} and \textbf{Single Write (update) Cost} defined in Table \ref{tab-properties} as mathematical metrics.

We use \textbf{Encoding Time}, \textbf{Decoding Time} and \textbf{Recovery Time} as the metrics in our experiments. Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes. Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes. Recovery time consists of computation time, I/O overhead and transmission time.
\subsubsection{Experiments Environment}
The environment of our experiments are shown in Table \ref{tab-platform}. We set a Hadoop system with one NameNode and $h$ DataNodes. Each DataNodes storage the data of one stripe of Approximate Code and the global parities are distributed at each DataNodes. We set $h=4,6$ and node size equal $1GB$ here as two default configurations. Our experiment can mainly be divided into four cases. First, we evaluate the encoding time for several erasure codes. Then we evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.

we performed the experiment of video frame recovery with the frame interpolation technique. The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}. We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes. We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data. The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio (PSNR).

\begin{table}[!ht]\small
\begin{tabular}{|l|l|}
\hline
Description & DELL R730 Server \\ \hline
CPU & Intel Xeon 3.0GHz \\ \hline
NIC 1Gbps & 1Gbps \\ \hline
Memory & 32GB \\ \hline
Disk & 8TB HDD \\ \hline
OS & Linux 3.19 \\ \hline
Platform & Hadoop HDFS 3.0.3 \\ \hline
\end{tabular}
\vspace{3mm}
\caption{Details of Our Evaluation Platform}\label{tab-platform}
\vspace{-10mm}
\end{table}

\subsection{Numerical Results of Mathematical Analysis}
In this section, we show the mathematical analysis of Approximate Code and compare it with STAR Code, TIP-Code, LRC and RS codes.
\begin{itemize}
    \item \textbf{Storage Overhead:} We compare the storage overhead between RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), where $h = 4$ or $6$. As shown in Figure \ref{fig-Storage}, the results shows that APPR.RS Code has much lower storage overhead than RS Code. The ratio of optimization is up to 21.4\% when $h=4, k=4$ and $23.8\%$ when $h=6, k=4$. For more typical configuration that $k=6$, APPR.RS ($6,1,2,4$) recude the number of parity nodes from $3$ to $1.33$.
    \item \textbf{Fault Tolerance:} The fault tolerance of Approximate Code is the same as the inputted erasure codes. All the erasure codes we evaluate in this Section are 3DFTs.
    \item \textbf{Single Write Performance:} We compare the single write performance between RS, STAR, APPR.RS and APPR.STAR, where $h = 4 or 6$. As shown in Figure \ref{fig-Sig-Write}, the results shows that APPR.RS Code has lower single write performance than RS Code and STAR Code. The ratio of optimization is up to $41.3\%$ when $h=6$ and $25\%$ when $h=4$. As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
\end{itemize}

\begin{figure}[ht]
\subfigure[h=4]{
    \label{fig-storage4}
    \includegraphics[width = 0.44\linewidth]{photo/experiment/Storage-4.eps}
}
\subfigure[h=6]{
    \label{fig-storage6}
    \includegraphics[width = 0.44\linewidth]{photo/experiment/Storage-6.eps}
}
\caption{Storage Overhead}\label{fig-Storage}
\end{figure}

\begin{figure}[ht]
\subfigure[h=4]{
    \label{fig-Sig-Write4}
    \includegraphics[width = 0.44\linewidth]{photo/experiment/Single-4.eps}
}
\subfigure[h=6]{
    \label{fig-Sig-Write6}
    \includegraphics[width = 0.44\linewidth]{photo/experiment/Single-6.eps}
}
\caption{Single Write Performance}\label{fig-Sig-Write}
\end{figure}

\subsection{Experimental Results and Analysis}
In this part, we compared the encoding and decoding time of Approximate Code with TIP-Code, STAR code, RS code and LRC codes, respectively. The code configuration is as follow,
\begin{itemize}
    \item We use ($k,1,2,4$), ($k,2,1,4$), ($k,1,2,6$) and ($k,2,1,6$) as the parameter used in the generation process of APPR.RS Code, APPR.TIP-Code and APPR.STAR Code. We also use ($k,1,2,4$) and ($k,1,2,6$) as the parameter used in generating APPR.LRC.
    \item \textbf{RS Code:} RS($k,3$). $k = 5,7,9,11,13$.
    \item \textbf{LRC Codes:} LRC ($k,4,3$), LRC ($k,6,3$). $k = 5,7,9,11,13$.
    \item \textbf{TIP-Code:} TIP($k,3$). $k = 5,9,11,15,17$.
    \item \textbf{STAR Code:} STAR($k,3$). $k = 5,7,11,13,17$.
\end{itemize}

\subsubsection{Encoding Time}
The results are shown in Figure \ref{fig-encoding}.
\begin{itemize}
    \item STAR Code: Approximate Code encodes faster than STAR code and the rate of optimization is up to $56.3\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).

    \item TIP-Code: the result of TIP-Code is similar to STAR code. The rate of optimization is up to 58.1\% (between APPR.TIP ($k,1,2,6$) and TIP ($k,3$) when $k$ = 9).

    \item RS Code: We could find out that the  (between APPR.RS ($k,1,2,6$) and RS($k,3$) when $k = 5$).

    \item LRC Codes: We could see that Approximate Code largely reduces the encoding time, comparing to LRC codes. The rate of optimization is up to 88.9\% (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
\end{itemize}

We combined the encoding time of five codes in Figure \ref{fig-BAR} with $k$=5. The results show that Approximate Code has the best encoding performance among five codes. There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while typical 3DFTs codes generate 3 nodes. (2) Approximate Code use XOR-based codes (TIP and STAR code) which have lower computational overhead than RS-based codes.\par

\begin{figure}[ht]
\subfigure{
    \label{fig-encodingSTAR}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-Star.eps}
}
\subfigure{
    \label{fig-encodingTIP}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-TIP.eps}
}
\subfigure{
    \label{fig-encodingRS}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-RS.eps}
}
\subfigure{
    \label{fig-encodingLRC}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-LRC.eps}
}
\vspace{-0.3cm}
\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}\vspace{-3mm}
\end{figure}

\subsubsection{Decoding Time under Single Node Failure Condition Analysis}
The results are shown in Figure \ref{fig-decoding-1}.
\begin{itemize}
    \item STAR Code: The decoding time of Approximate Code is almost the same as STAR code when sinlge node fails and the rate of optimization is up to 5.4\% (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
    \item TIP-Code: The decoding time of Approximate Code is almost the same as TIP-Code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code. The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
    \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node. The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
\end{itemize}

We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-BAR} with $k=5$. The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same. The main reason is that XOR-based codes have lower computational overhead than RS-based codes.\par

\begin{figure}[ht]
\subfigure{
    \label{fig-decoding-1-STAR}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-Star.eps}
}
\subfigure{
    \label{fig-decoding-1-TIP}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-TIP.eps}
}
\subfigure{
    \label{fig-decoding-1-RS}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-RS.eps}
}
\subfigure{
    \label{fig-decoding-1-LRC}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-LRC.eps}
}
\vspace{-0.3cm}
\caption{Decoding Time Comparison in Single Node Failure between Approximate Code and other method}\label{fig-decoding-1}\vspace{-3mm}
\end{figure}

\subsubsection{Decoding Time under Double Node Failure Condition Analysis}
The results are shown in Figure \ref{fig-decoding-2}.
\begin{itemize}
    \item STAR Code: The rate of optimization is up to $83.9\%$ (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
    \item TIP-Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
    \item RS Code: We could find out that the Approximate Code decodes largely faster than RS code under two failure nodes condition. The rate of optimization is up to $96.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
    \item LRC Codes:
    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes. The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
\end{itemize}

>>>>

To address this challenge, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems. The key idea of Approximate Code is distinguishing the important and unimportant data with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to ensure high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, LRC, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\% and increase the recovery speed by up to 4.7X when double nodes fail.
\end{abstract}

@@

\section{Introduction}
For typical cloud storage systems such as Windows Azure \cite{calder2011windows} and Amazon AWS \cite{bermudez2013exploring}, erasure coding is a popular technique to provide both high reliability and low monetary cost \cite{EVENODD, RDP, BlaumRoth, XCode, CRS, TripleStar, TPtech, RSL}, where triple disk failure fault tolerant arrays (3DFTs) are widely used. Typical erasure codes can be divided into two categories, RS-based Codes \cite{RS} \cite{LRC} and XOR-based codes \cite{EVENODD, hcode, STAR, TIP}. RS-based codes are encoded based on the Galois Field(GF) Computation \cite{RS}, which allow flexible configuration and have a little higher computation cost. XOR-based codes simplify the computation, but they suffer other issues like scalability \cite{wu2012sdm, jiang2016bdr}.

@@

STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star}.
In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which leads to a long parity chain.

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} For example, in the diagonal parity $S = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S$.]{
\includegraphics[height=6.3cm, width = 3.8cm]{photo/STAR.pdf}\label{fig-star}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} For example, in the horizontal parity $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$]{
\includegraphics[height=6.3cm, width = 3.8cm]{photo/TIP.pdf}\label{fig-TIP}
}\vspace{-3mm}
\caption{\small{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-TIP}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$.}}
\vspace{-3mm}
\label{fig-star-TIP}
\end{figure}

TIP-Code is also an XOR-based 3DFTs erasure code, as shown in Figure \ref{fig-TIP}.
Compared with STAR code, the parities are generated independently, which reduces the number of I/O operations for partial stripe writes.

@@

\begin{table}[ht]\small
\centering
\caption{
Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|p{1.8cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.4cm}<{\centering}|}
\hline
Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
Data Compression & low & / & high & Application Level\\ \hline
RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
RAID-6 & low & low & low & \\ \cline{1-4} 
RAID-5 & medium & medium & low & \\ \cline{1-4} 
Approximate Storage & very low & very low & low & \\ \cline{1-4} 
Approximate Code & low & high & low & \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=0.83\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}\label{fig-framework}
\end{figure*}

@@

\subfigure[The generation of APPR.LRC ($4,2,2,3$,Even)]{
    \includegraphics[width=0.75\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
}
\caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
\end{figure}

@@

\begin{figure}[ht]
\centering
\subfigure[Structure selection.]{
    \label{fig-ap-TIP-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-STAR-STR.pdf}
}

\subfigure[Generation of APPR.STAR.]{
    \label{fig-ap-TIP-GEN}
    \includegraphics[width = 0.95\linewidth]{photo/APPR-STAR-GEN.pdf}
}
\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}\label{fig-appr-star}
\end{figure}

\begin{figure}[ht]
\centering
\subfigure[Structure selection of APPR.TIP-Code]{
    \label{fig-ap-TIP-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
}
\hspace{2pt}
\subfigure[Generation of local parities]{
    \label{fig-ap-TIP-lP}
    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
}

\subfigure[Generation of global parities]{
    \label{fig-ap-TIP-GP}
    \includegraphics[width = 0.9\linewidth]{photo/APPR-TIP-GL-v2.pdf}
}
\vspace{-3mm}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}\label{fig-ap-TIP}
\vspace{-3mm}
\end{figure}

@@

\section{Evaluation}\label{evaluation}
In this section, we conduct a series of experiments to demonstrate the efficiency of Approximate Code framework.

\subsection{Evaluation Methodology}
The experiments consist of two parts. The first part we evaluate the performance/reliability of the Approximate Code, which include encoding/decoding performance, single write performance, etc. The second part we verify the capability of interpolation algorithm to recover the lost video frames. The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}. We define a $1\%$ data loss on the unimportant video frames. The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio (PSNR).

%In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code. Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.

%In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.

\subsubsection{Erasure Codes}
We select several erasure codes and their corresponding approximate codes in our evaluation as below ($k = 5,7,9,11,13,15,17$), which can tolerant concurrent triple node failures and be used in typical cloud storage systems.
\begin{itemize}
    \item \textbf{Approximate Code:} APPR. RS/LRC/TIP/STAR ($k,1,2,4$), APPR. RS/LRC/TIP/STAR ($k,1,2,6$). If an approximate code has two structures (Even/Uneven), we use the average value as the result in our comparison.
    \item \textbf{RS Code \cite{RS}:} RS($k,3$).
    \item \textbf{LRC Codes \cite{LRC}:} LRC ($k,4,3$), LRC ($k,6,3$). 
    \item \textbf{TIP Code \cite{TIP}:} TIP($k,3$). 
    \item \textbf{STAR Code \cite{STAR}:} STAR($k,3$).
\end{itemize}

\subsubsection{Metrics}
We select the \textbf{Storage Overhead}, \textbf{Single Write Cost}, \textbf{Encoding Time}, \textbf{Decoding Time} and \textbf{Recovery Time} as the metrics in our evaluation.

Storage overhead is the ratio between the total amount of data (all data and parities) and the original data. Single write cost is the average number of I/O operations to handle a single write. Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes. Recovery time is the total number to recover a lost data, which consists of computation time, I/O overhead, transmission time, etc.

\subsubsection{Experimental Environment}
The experimental environment is shown in Table \ref{tab-platform}. We set a Hadoop system with one NameNode and $h$ DataNodes. Each DataNodes are the same as data nodes in Approximate Code, and the global parities are distributed on each DataNodes. We set $h=4,6$, and the size of each node is $1GB$.

%Our experiment can mainly be divided into four cases. First, we evaluate the encoding time for several erasure codes. We then evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.

\begin{table}[!ht]\footnotesize
\begin{tabular}{|l|l|}
\hline
Description & DELL R730 Server \\ \hline
CPU & Intel Xeon 3.0GHz \\ \hline
NIC & 10Gbps \\ \hline
Memory & 32GB \\ \hline
Disk & 8TB HDD \\ \hline
OS & Linux 3.19 \\ \hline
Platform & Hadoop HDFS 3.0.3 \\ \hline
\end{tabular}
\caption{Details of Our Evaluation Platform}\label{tab-platform}
\vspace{-4mm}
\end{table}

\subsection{Mathematical Analysis}
In this section, we show the numerical results of mathematical analysis by comparing the Approximate Code with its corresponding original code.

\begin{itemize}
    \item \textbf{Storage Overhead:} We compare the storage overhead among RS ($k,3$), APPR.RS ($k,1,2,h$) and APPR.RS ($k,2,1,h$), and the results are shown in Figure \ref{fig-Storage}. It is clear that APPR.RS has much lower storage overhead than RS Code. The degradation is up to 21.4\% when $h=4, k=4$, and $23.8\%$ when $h=6, k=4$. When $k=6$, APPR.RS ($6,1,2,4$) reduces the average number of parity nodes from $3$ to $1.33$.
    \item \textbf{Single Write Performance:} We compare the single write cost among different erasure codes, and the results are shown in Figure \ref{fig-Sig-Write}. We notice that APPR.RS has the lowest single write performance, which decreases the average number of I/Os by up to  $41.3\%$. 
%The ratio of optimization is up to $41.3\%$ when $h=6$ and $25\%$ when $h=4$. As $k$ increases, the performance of APPR.STAR is close to RS and always better than STAR.
\end{itemize}

\begin{figure}[ht]
\subfigure[h=4]{
    \label{fig-storage4}
    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-4.eps}
}
\subfigure[h=6]{
    \label{fig-storage6}
    \includegraphics[width = 0.42\linewidth]{photo/experiment/Storage-6.eps}
}
\caption{Storage overhead comparison between RS and APPR.RS}\label{fig-Storage}
\end{figure}

\begin{figure}[ht]
\subfigure[h=4]{
    \label{fig-Sig-Write4}
    \includegraphics[width = 0.42\linewidth]{photo/experiment/Single-4.eps}
}
\subfigure[h=6]{
    \label{fig-Sig-Write6}
    \includegraphics[width = 0.42\linewidth]{photo/experiment/Single-6.eps}
}
\caption{Single write performance comparison among RS, STAR, APPR.RS and APPR.STAR.}\label{fig-Sig-Write}
\end{figure}

\subsection{Experimental Results}
In this subsection, we show the experimental results of various codes in terms of encoding/decoding time and recovery time.

\subsubsection{Encoding Time}
The results are shown in Figure \ref{fig-encoding}.
\begin{itemize}
    \item Compared to STAR/TIP Codes: Approximate Code encodes faster than STAR/TIP code by up to $51.7\%$, $54.3\%$, respectively.

 %. (between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).

 %   \item Compare to TIP Code: The acceleration over original TIP code is similar to STAR code. The enhancement is up to $58.1\%$ (between APPR.TIP($k,1,2,6$) and TIP($k,3$) when k = 9).

    \item Compared to RS/LRC Code: Approximate Code improve the encoding significantly. The optimization ratios are up to $54.0\%$ for RS code,  $61.7\%$ for LRC codes, respectively.

 %(between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).

 %   \item Compare to LRC Codes: We could see that Approximate Code largely reduces the encoding time, comparing to LRC codes. The rate of optimization is up to $88.9\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC($k, 6, 2$) when $k = 5$).
\end{itemize}

%There are two reasons for this condition: (1) Approximate Code only generates $r+g/h$ parity nodes for each stripe, while tipical 3DFTs codes generate 3 nodes. (2) Approximate Code use XOR-based codes (TIP and STAR code) which have lower computational overhead than RS-based codes.\par

\begin{figure}[ht]
\subfigure{
    \label{fig-encodingSTAR}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-Star.eps}
}
\subfigure{
    \label{fig-encodingTIP}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-TIP.eps}
}
\subfigure{
    \label{fig-encodingRS}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-RS.eps}
}
\subfigure{
    \label{fig-encodingLRC}
    \includegraphics[width = 0.46\linewidth]{photo/experiment/Encoding-LRC.eps}
}
\vspace{-0.3cm}
\caption{Encoding Time Comparison among various erasure coding methods.}\label{fig-encoding}
\end{figure}

\subsubsection{Decoding Time under Single Node Failure Condition}
The results are shown in Figure \ref{fig-decoding-1}.
\begin{itemize}
    \item Compared to STAR/TIP Codes: The decoding time of Approximate Code is almost the same as original code when single node fails, with an increment by up to $5.5\%$ for STAR code, up to $10.8\%$ for TIP Code, respectively.
  %   (between APPR.STAR ($k,1,2,4$) and STAR ($k,3$) when $k = 5$).
 %   \item TIP Code: The decoding time of Approximate Code is almost the same as TIP code when sinlge node fails and the rate of optimization is up to 8.8\% (between APPR.TIP($k,1,2,4$) and TIP($k,3$) when k = 17).
    \item Compared to RS/LRC Codes: Approximate Code decodes nearly the same as RS code (improvement by up to $0.9\%$) and LRC codes (enhancement by up to $1.3\%$). In some scenarios, approximate codes are worse than original codes, which is affected by small differences on parameter configurations.
    \item In some scenarios, approximate codes are worse than original codes, which is affected by small differences on parameter configurations.
 %The rate of optimization is up to 80.2\% (between APPR.TIP/STAR ($k,1,2,4$) and RS($k,3$) when $k = 5$).
  % \item LRC Codes: We could see that Approximate Code and LRC codes have no big gap when encoding one lost node. The rate of optimization is up to $5.8\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 13$).
\end{itemize}

%We combined the decoding time of five codes under one failure node condition in Figure \ref{fig-BAR} with $k=5$. The results show that RS code has the worst one node decoding performance among five codes and the performance of other four codes are almost the same. The main reason is that XOR-based codes have lower computational overhead than RS-based codes.\par

\begin{figure}[ht]
    \subfigure{
        \label{fig-decoding-1-STAR}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-Star.eps}
    }
    \subfigure{
        \label{fig-decoding-1-TIP}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-TIP.eps}
    }
    \subfigure{
        \label{fig-decoding-1-RS}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-RS.eps}
    }
    \subfigure{
        \label{fig-decoding-1-LRC}
        \includegraphics[width = 0.46\linewidth]{photo/experiment/Decoding-1-LRC.eps}
    }
    \vspace{-0.3cm}
    \caption{Single Node Decoding Time Comparison among various erasure coding methods.}\label{fig-decoding-1}
    \end{figure}

\subsubsection{Decoding Time under Double Nodes Failure Condition}
The results are shown in Figure \ref{fig-decoding-2}.
\begin{itemize}
    \item Compared to STAR/TIP Codes: The recovery acceleration is up to $76.5\%$ for STAR, up to $77.6\%$, respectively.
    %((between APPR.STAR ($k,1,2,6$) and STAR ($k,3$) when $k = 5$).
    %\item TIP Code: This condition is similar to STAR code. The rate of optimization is up to $84.8\% $(between APPR.TIP($k,1,2,6$) and TIP($k,3$) when $k = 9$).
    \item Compared to RS/LRC Codes: Approximate Code reconstruct the lost data faster than original erasure codes, which improve the reconstruction by up to $75.4\%$ for RS code, and $78.7\%$ for LRC codes, respectively.
    %(between APPR.TIP/STAR ($k,1,2,6$) and RS($k,3$) when $k = 5$).
%    \item LRC Codes:
%    We could see that Approximate Code largely reduces the decoding time when two nodes fail, compared with LRC codes. The rate of optimization is up to $97.2\%$ (between APPR.TIP/STAR ($k,1,2,6$) and LRC ($k, 6, 2$) when $k = 5$).
\end{itemize}
